### 2015-05-21 paper.tex
Initial draft

\documentclass{article}

\usepackage{cite}

\begin{document}
\input{macro}

\title{Declarative Data Analytic}
\author{}

\maketitle

\section{Summary for \saf}
\label{sec:saf}

\subsection{Paper}
\label{sec:safpaper}

\paragraph{Overview.}
The purpose of \saf\cite{arun2011} is to bridge the semantic gap between raw
data and the user's high-level view of the system. \saf achieves the goal by
introducing {\em behavior model} --- a logic-based abstraction that allows the user to
concisely specify desired relationship between different events of the system --- along
with a low-level implementation that maps user-defined behaviors (i.e., logic
formulas) to satisfying log traces.

\paragraph{Implementation.}
The implementation is composed of five components: 
(1) knowledge base, which provides domain-specific knowledge pre-specified as behavior
models; 
(2) data normalizer, which normalizes data from different sources into unified
events --- an internal data model for storage and query.
(3) event storage, an SQL database storing events.
(4) analysis engine, which takes a user-specified behavior model as input, and
extracts the satisfying set of events (or event sequences) based on defined
semantics.
(5) presentation engine, an output system.

\paragraph{Comments.}
\begin{itemize}
\item Is the specification for exact time comparison useful? Due to possible
  clock shift between different devices in a distributed system, the timestamps
  in logs extracted from different devices may not be comparable at all. I
  believe relative time ordering makes more sense in a network.

\paragraph{Questions.}
\begin{itemize}
\item What
\end{itemize}

\end{itemize}

\subsection{\saf tool}
\label{sec:saftool}

\bibliography{paper}{}
\bibliographystyle{plain}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-05-27 paper.tex
Change questions

@@
   believe relative time ordering makes more sense in a network.
-
-\paragraph{Questions.}
-\begin{itemize}
-\item What
-\end{itemize}
-
 \end{itemize}
@@
 \label{sec:saftool}
+
+\begin{itemize}
+\item Tutorial finished: I have tried the example TCP records on the \saf
+  website, and generated the traces that satisfy the three-way-handshake
+  behavior.
+\item Trying \saf on real-data now...
+\end{itemize}
+
+\subsection{A root cause localization model for large scale systems}
+\label{sec:rootcause}
+
+The paper presents a model capturing essential features of the root cause
+localization process. In the model, a system is modeled as a set of components
+that interact with each other. Observable behaviors of the system are modeled as
+quarks --- the smallest end-to-end observable unit of specific service. Each
+quark is composed of:
+(1) the set of components used by the quark (could be implemented as a list); and
+(2) a health result, signifying the failure or the success of the quark. (could
+be implemented as a boolean variable).
+
+Partial failure is modeled with probability: Given a component $C_i$,
+probability $p_i$ represents the failure probability of a quark that utilizes
+component $C_i$.
+
+The paper further defines the problem of root cause localization, which has two
+versions: deterministic version and statistical version. Only the deterministic
+version is relevant to our project: Given several quarks of the system, some of
+which succeed and others fail, estimate the set of components that could have partial
+failure i.e., list of components $C_i$ with $p_i > 0$.
+
+\paragraph{Comments}
+
+\begin{itemize}
+\item Is failure always modeled using probability? What are other possible
+  failure models?
+\end{itemize}
 

### 2015-05-27 paper.tex
Add questions

@@
 
-\section{Summary for \saf}
+\section{\saf}
 \label{sec:saf}
@@
 
+\paragraph{Progress.}
+
 \begin{itemize}
@@
 \item Trying \saf on real-data now...
+\end{itemize}
+
+\paragraph{Questions:}
+
+\begin{itemize}
+\item Are GISP\_Original, Thin\_client\_environment and Tamagawa related data? 
+\item Do all of them contain anomalies? 
+\item What has been done to diagnose/solve the anomalies, if any?
+
 \end{itemize}
@@
 
+\section{Project}
+\label{sec:project}
+
+\subsection{Goal}
+\label{sec:proj:goal}
+Help the user to define failure models of systems, so that the failure model
+could help identify the root cause of anomalies.
+
 \bibliography{paper}{}

### 2015-05-27 paper.tex
Add meeting summary

--- 2015-05-27 paper.tex
@@
   behavior.
-\item Trying \saf on real-data now...
+\item Trying \saf on real-data now... (Detailed information of the data is in
+  the email).
 \end{itemize}
+
+\paragraph{Questions:}
 
@@
 
+\section{Project}
+\label{sec:project}
+
+\subsection{Goal}
+\label{sec:proj:goal}
+% Help the user to define failure models of systems, so that the failure model
+% could help identify the root cause of anomalies.
+
+Develop a declarative language that allows the user to specify/query the root
+cause of a system anomaly, so that the user does not need to handle low-level
+logging data directly.
+
+\section{Meeting Log}
+\label{sec:meetlog}
+
+\subsection{5/27}
+
+We discussed about the skeleton of the project. The problem is much clearer
+after the meeting. The goal of the project, at this stage, is to develop a
+declarative language that helps a network administrator to specify/query the root cause of a
+system problem, given overwhelming log information.
+
+\paragraph{Questions}
+
+\begin{itemize}
+\item What are the current status of network diagnosis?
+\item What is a good abstraction of root cause analysis?
+\end{itemize}
+
+\section{Reading List}
+\label{sec:read}
+
+Troubleshooting Blackbox SDN Control Software with Minimal Causal
+Sequences. (link: http://www.eecs.berkeley.edu/~rcs/research/sts.pdf)
+
+Fault Management in Distributed Systems. (link:
+http://repository.upenn.edu/cgi/viewcontent.cgi?article=1960&context=cis_reports)
+
 \bibliography{paper}{}

### 2015-06-04 paper.tex
Summary on 6/3 meeting

@@
 \usepackage{cite}
+\usepackage{url}
 
@@
 
-\section{\saf}
+\section{Project}
+\label{sec:project}
+
+\subsection{Motivation}
+\label{sec:motiv}
+
+Existing root cause analysis techniques assume the availability of a known
+causality model. However, a network administrator may not have a complete
+knowledge of all the causality relationships in the system (Examples?). In
+certain cases, the only available information is the logging history of a
+system. Therefore, a framework that allows the administrator to easily
+create, manipulate and query dependency information is of great help. The
+framework should also provide a friendly interface that fits the administrator's
+high-level understanding of the system. In addition, the framework should also
+enable the administrator to easily carry out root cause analysis, given the
+dependency information and the logging history.
+
+% \subsection{Goal}
+% \label{sec:proj:goal}
+% Help the user to define failure models of systems, so that the failure model
+% could help identify the root cause of anomalies.
+
+% Develop a declarative language that allows the user to specify/query the root
+% cause of a system anomaly, so that the user does not need to handle low-level
+% logging data directly.
+
+\section{Meeting Log}
+\label{sec:meetlog}
+
+\subsection{5/27}
+
+We discussed about the skeleton of the project. The problem is much clearer
+after the meeting. The goal of the project, at this stage, is to develop a
+declarative language that helps a network administrator to specify/query the root cause of a
+system problem, given overwhelming log information.
+
+\subsection{6/3}
+\label{sec:meeting:63}
+
+\paragraph{Progress}
+\begin{itemize}
+\item Read the paper ``A survey of fault localization techniques in computer
+networks'': They summarized a number of techniques that find the root cause of a
+system error with a given causality graph.
+
+\item Read the paper ``Efficient Querying and Maintenance of Network Provenance at
+Internet-Scale'': They proposed a graph-based data structure to maintain network
+provenance, i.e., dependency relationship. Also, different forms of
+representation for specifying the causal relationship were given, such as
+algebraic representation and BDD.
+
+\item Scan through the NEC network data.
+\end{itemize}
+
+\paragraph{Meeting summary.}
+In the meeting, we further clarified the problem.
+
+In the current design, our framework takes two inputs:
+(1) a set of logs from the network (format undefined); and
+(2) a detected anomaly (format undefined).
+
+The output of the framework is the root cause that could explain the detected
+anomaly. The format of the root cause is also unknown now (could be an event or
+a set of events).
+
+Within the framework, we have a library which stores behavior
+models (i.e., causal relationship). There will also be a root cause analysis
+engine that is responsible
+for generating the root cause based on the anomaly, the logs and the
+library. A possible design for the root cause analysis engine
+could be first to find the behavior models that have the anomaly as root---These
+models are called failure models for the anomaly---then the
+engine finds all log sequences satisfying the behavior model (we can
+leverage \saf{} for this part), and runs the root cause analysis algorithm on
+the log sequences found.
+
+The behavior library needs to be specified by the user---it is almost impossible
+to infer the behavior models without human input---and a language is needed for
+the user to specify, manipulate, and query the library. The language could be any
+existing language, such as \saf{} and Datalog, or a newly designed one.
+
+\paragraph{To-do}
+\begin{itemize}
+\item More survey on the root cause analysis is needed. The focus would be on
+  (1) What's the current status of root cause analysis?; (2) whether anyone has
+  tried to manage causality as a database? If so, how did they do it?
+\item The real data is worth further exploration. Hopefully we can have more
+  insight from the data.
+\end{itemize}
+
+\section{Reading List}
+\label{sec:read}
+
+\begin{itemize}
+
+\item Troubleshooting Blackbox SDN Control Software with Minimal Causal
+Sequences. (link: \url{http://www.eecs.berkeley.edu/~rcs/research/sts.pdf})
+
+\item Fault Management in Distributed Systems. (link:
+\url{http://repository.upenn.edu/cgi/viewcontent.cgi?article=1960&context=cis_reports})
+
+\item A survey of fault localization techniques in computer networks. (link: \url{http://www.eecis.udel.edu/~sethi/papers/04/socp04.pdf})
+
+\end{itemize}
+
+\section{\saf{}}
 \label{sec:saf}
@@
 \paragraph{Overview.}
-The purpose of \saf\cite{arun2011} is to bridge the semantic gap between raw
-data and the user's high-level view of the system. \saf achieves the goal by
+The purpose of \saf{}~\cite{arun2011} is to bridge the semantic gap between raw
+data and the user's high-level view of the system. \saf{} achieves the goal by
 introducing {\em behavior model} --- a logic-based abstraction that allows the user to
@@
 
-\subsection{\saf tool}
+\subsection{\saf{} Tool}
 \label{sec:saftool}
@@
   behavior.
-\item Trying \saf on real-data now... (Detailed information of the data is in
+\item Trying \saf{} on real-data now... (Detailed information of the data is in
   the email).
@@
 
-The paper presents a model capturing essential features of the root cause
+The paper (bib not found online) presents a model capturing essential features of the root cause
 localization process. In the model, a system is modeled as a set of components
@@
 
-\section{Project}
-\label{sec:project}
-
-\subsection{Goal}
-\label{sec:proj:goal}
-% Help the user to define failure models of systems, so that the failure model
-% could help identify the root cause of anomalies.
-
-Develop a declarative language that allows the user to specify/query the root
-cause of a system anomaly, so that the user does not need to handle low-level
-logging data directly.
-
-\section{Meeting Log}
-\label{sec:meetlog}
-
-\subsection{5/27}
-
-We discussed about the skeleton of the project. The problem is much clearer
-after the meeting. The goal of the project, at this stage, is to develop a
-declarative language that helps a network administrator to specify/query the root cause of a
-system problem, given overwhelming log information.
-
-\paragraph{Questions}
-
-\begin{itemize}
-\item What are the current status of network diagnosis?
-\item What is a good abstraction of root cause analysis?
-\end{itemize}
-
-\section{Reading List}
-\label{sec:read}
-
-Troubleshooting Blackbox SDN Control Software with Minimal Causal
-Sequences. (link: http://www.eecs.berkeley.edu/~rcs/research/sts.pdf)
-
-Fault Management in Distributed Systems. (link:
-http://repository.upenn.edu/cgi/viewcontent.cgi?article=1960&context=cis_reports)
-
 \bibliography{paper}{}

### 2015-06-15 paper.tex
Minor updates
6/15 update

@@
 system. Therefore, a framework that allows the administrator to easily
-create, manipulate and query dependency information is of great help. The
+create, update, manipulate and query dependency information is of great help. The
 framework should also provide a friendly interface that fits the administrator's
@@
 \item Scan through the NEC network data.
+\end{itemize}
+
+\paragraph{6/9}
+
+We further discussed about the contributions we can make in our project. It now
+seems that a promising direction is to explore efficient interactive causal
+relationship generation. The causal relationship may be heterogeneous---that is,
+the user can specify causal relationship at different level of granularity. Details can be found in 6/9 meeting slides.
+
+Future steps:
+
+\begin{itemize}
+\item Related work survey: Does there exist any work that provides similar
+  management?
+
+A: Causality of an event can be modeled as a directed tree. A causality group is a set of
+partial order, which can be represented as a DAG. The DAG can be implemented as
+an adjacency graph, stored in a database.
+\item Low-level operation of a command in the declarative language?
+
+A: 
+\begin{itemize}
+\item Insert($A \rightarrow B$): check if there is a path such that $B
+  \rightarrow A$. If
+not, add an adjacency link ($A \rightarrow B$) in the adjacent
+graph. Otherwise, raise an error.
+\item Delete($A \rightarrow B$): Delete the corresponding link in the adjacency
+  graph.
+\item Update($A \rightarrow B$ to $A \rightarrow C$): Delete($A \rightarrow B$)
+  followed by insert($A \rightarrow C$).
+\item Manipulate($A \rightarrow B$): Compose? Should also happen at the event level.
+\end{itemize}
+
+\item Details of the work flow: the steps the user could take to finish the
+  modeling.
+\item Connect SAF with ElasticSearch: decouple SAF from SQLite, and use restful
+  api as the query language.
 \end{itemize}

### 2015-07-02 paper.tex
Meeting log for 7/1

@@
 \usepackage{url}
+\usepackage[normalem]{ulem}
+\usepackage{color}
 
@@
 for generating the root cause based on the anomaly, the logs and the
-library. A possible design for the root cause analysis engine
+library. 
+(\textcolor{red}{Root cause analysis engine is only used for case study.6/24}) 
+\sout{A possible design for the root cause analysis engine
 could be first to find the behavior models that have the anomaly as root---These
@@
 leverage \saf{} for this part), and runs the root cause analysis algorithm on
-the log sequences found.
+the log sequences found. }
 
-The behavior library needs to be specified by the user---it is almost impossible
+The behavior library needs to be specified by the user (\textcolor{red}{or the
+  domain-specific expert. 6/25}) ---it is almost impossible
 to infer the behavior models without human input---and a language is needed for
-the user to specify, manipulate, and query the library. The language could be any
-existing language, such as \saf{} and Datalog, or a newly designed one.
+the user to specify, manipulate, and query the library. \sout{The language could be any
+existing language, such as \saf{} and Datalog, or a newly designed one.}
 
@@
   insight from the data.
+\end{itemize}
+
+\paragraph{6/24}
+
+In today's meeting, I gave a survey on three commercial solutions for root
+cause analysis through log
+analytics---namely HP solution, CA technology solution and IBM solution. Among
+the three solutions, HP solution provides guidance on the work flow
+for root cause analysis. CA technology is similar to SAF, and their event rule
+idea is helpful in our project. IBM solution, however, is closer to a
+search-filter analytic tool, which allows the administrator to plot different
+statistical graphs based on the logs. More details can be found on the slides
+for the weekly meeting on June 24.
+
+The design of the declarative language for our project was further discussed in
+the meeting. The language should extend the design of SAF. In SAF, a behavior is merely
+a set of events. This is not enough for a complex and heterogeneous computing
+environment. In such an environment, users' knowledge of the system could vary among different
+levels. For example, a domain-specific expert could be more familiar with a
+certain types of devices, such as database servers or email servers, while a
+network administrator could know more about the protocol-level information along with
+topological information. Our language should provide the opportunity for
+different users to specify their specific knowledge of the system, and manages these
+knowledge effectively in the storage, so that root cause analysis can be
+performed with these knowledge.
+
+\paragraph{To-do}
+
+\begin{itemize}
+\item Detailed work flow of the user.
+\item Connect SAF with ElasticSearch: decouple SAF from SQLite, and use restful
+  api as the query language.
+\item Survey on languages that allow the user to specify causality relationship
+  on different granularity.
+A: Ontology is an interesting concept. 
+\end{itemize}
+
+\paragraph{7/1}
+
+In today's meeting, we clarify the work flow of performing root cause analysis
+in a typical network, and the problem to be targeted at during my summer
+internship. Additionally, we discussed about the next few steps of the project
+towards our goal.
+
+\begin{itemize}
+\item {\bf Word flow.} The work flow of the root cause analysis is as follows:
+  \begin{itemize}
+  \item The user reports an abnormal symptoms to the network administrator. The
+  abnormal symptoms include high latency or no response of a specific
+  service. The user usually specify such symptoms informally, such as in natural
+  languages.
+  \item Next, the network administrator would start the root cause analysis by
+  collecting log traces from all the devices in the network. Since devices could
+  be manufactured by different vendors, the logs could be in a variety of forms.
+  \item To allow for computer-aided log analysis, the network administrator should
+  be able to convert logs of different formats into a unified one
+  (e.g. relational database).
+  \item With the unified log database, the network administrator should be
+  able to specify the symptoms reported by the user rigorously. A failure symptom
+  could be formally defined as a set of database entries, or events. 
+  \item In addition to the symptom specification and the log traces, the network
+  administrator still needs network provenance (i.e., dependency relationship
+  between events or set of events) to help identify the root cause
+  analysis. In the usual scenario of log analytics, the network provenance is not
+  given beforehand. The network administrator needs to infer the provenance
+  information based on his domain-specific knowledge, such as topological
+  layout.
+  \item The network administrator would then run the root cause analysis algorithm
+  based on the given symptom and the provenance information to identify the root
+  cause of the system anomaly. 
+  \end{itemize}
+
+\item {\bf Targeted problem.}
+  The targeted problem scope of our project is the part of provenance knowledge
+  maintenance. It is assumed that the log has been organized into a uniform format
+  (e.g., relational database), and basic database queries are available (e.g.,
+  through SQL language). The goal is to have a framework that allows the user to
+  specify, query, validate and operate on semantic provenance --- The semantic level could
+  be flexible \textcolor{red}{more clear on what semantic level means}.
+
+  There are several requirements worth considering:
+  \begin{itemize}
+  \item The framework should be able to map the specified semantic provenance to
+    corresponding low-level semantics, where the lowest-level semantics is the
+    log traces.
+
+  \item The knowledge base should have categorization. For example, topological
+    knowledge should be differentiated from protocol knowledge. Protocol
+    knowledge could be reused across systems, but topological knowledge cannot.
+
+  \item 
+  \end{itemize}
+
   \end{itemize}
@@
 
-\item A survey of fault localization techniques in computer networks. (link: \url{http://www.eecis.udel.edu/~sethi/papers/04/socp04.pdf})
+\item A survey of fault localization techniques in computer networks. (link:
+  \url{http://www.eecis.udel.edu/~sethi/papers/04/socp04.pdf})
+
+\item Root cause analysis in market products:
+
+  \begin{itemize}
+  \item The 4 Building Blocks of Root Cause Analysis
+    (\url{http://apmdigest.com/the-4-building-blocks-of-root-cause-analysis}): The
+    best practice is to unify the three layers into a single infrastructure
+    management dashboard, so you can visually correlate all three levels of
+    analytics in an efficient workflow.
+  \item HP Operations Analytics (\url{https://www.youtube.com/watch?v=d3_r9-tFISk})
+  \item Hui Zhang's email (6/15)
+  \end{itemize}
+
+\item Knowledge Discovery in Databases: An Overview 
+(\url{https://mitpress.mit.edu/sites/default/files/titles/content/9780262660709_sch_0001.pdf})
+
+\item Semantic Data Access to Relational Databases: IBM research
+(\url{http://www.w3.org/wiki/images/9/90/Rdb2RdfXG$SeDA2RDB2RDFXG.pdf})
 

### 2015-07-15 paper.tex
Openstack case study

@@
 
-\paragraph{6/9}
+\subsection{6/9}
+\label{sec:meeting:69}
 
@@
 
-\paragraph{6/24}
+\subsection{6/24}
+\label{sec:meeting:624}
 
@@
 
-\paragraph{7/1}
+\subsection{7/1}
+\label{sec:meeting:624}
 
@@
 
-  \item 
   \end{itemize}
 
+\end{itemize}
+
+\paragraph{Future work}
+Complete a root cause analysis case study on OpenStack.
+
+\subsection{7/8}
+\label{sec:meeting:678}
+
+\paragraph{Thought}
+I wonder if component-level dependency can also be specified in \saf{}. Because no
+matter what dependency level we focus on, we still need to determine the
+low-level logs by specifying the conditions over their fields. The higher level the
+specification is, the more wildcard we are inserting into the specification.
+
+For example, if we would like to specify a component-level dependency: $vm_1
+\rightarrow vm_2$, we need to make it clear what logs are instances of $vm_1$
+and $vm_2$. To do this, a candidate specification would be ``machine\_name =
+$vm_1$. This specification is still in the scope of \saf{}. Based on this, the
+specification over the logs is similar to specification over the directory paths
+in the file system.
+
+\paragraph{Todo}
+
+\begin{itemize}
+\item Finish the manual root cause analysis case study.
+\item Meanwhile, clarify the work flow of the user.
+\item Find as much automation as possible in the work flow. For example,
+  automatic model generation.
+\end{itemize}
+
+\section{Root cause analysis case studies}
+Manual root cause analysis case studies.
+
+\begin{itemize}
+\item Backtracking the execution according to causality relationship
+  \begin{itemize}
+  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
+  \item Convert the log in JSON into an SQLite3 database. (done)
+  \item Obtain domain-specific knowledge about OpenStack and the execution:
+    data/models(Filtered Message Sequence)
+  \item Specify the domain-specific knowledge in SAF --- on different levels ---
+    and found corresponding traces.
+    \begin{itemize}
+    \item Level 1: event dependency
+    \item Level 2: component dependency
+    \end{itemize}
+  \item Build the causality graph for different levels.
+  \end{itemize}
+\item Root cause detection of failure symptoms based on the backtracking technique
 \end{itemize}

### 2015-07-15 codebase/case_study/json_to_sqlite.py

@@ -1,0 +1,54 @@
+# -*- coding: utf-8 -*-
+
+import json
+import sqlite3
+
+json_file = "delete-0.log"
+sqlite_file = "delete.db"
+
+traffic = json.load(open(json_file))
+db_conn = sqlite3.connect(sqlite_file)
+
+# Get database schema
+sample_entry = traffic[0]
+key_list = sample_entry.keys()
+# Get rid of '@' in the key
+for n,key in enumerate(key_list):
+    if key.startswith('@'):
+        new_key = key.replace('@', 'aT')
+        key_list[n] = new_key
+key_count = len(key_list)
+key_string = ', '.join(key_list)
+
+#print key_count
+#print key_string
+
+# Create the database table
+# TODO: avoid hardcoding table schemas
+cursor = db_conn.cursor()
+table_name = 'network_log'
+deletion_query = 'drop table if exists ' + table_name
+cursor.execute(deletion_query)
+creation_query = 'create table ' + table_name + ' (' + key_string + ')'
+#print creation_query
+cursor.execute(creation_query)
+
+# Data insertion template
+placeholders = ['?'] * key_count
+placeholder_string = ', '.join(placeholders)
+data_insertion = 'insert into ' + table_name + ' values(' + placeholder_string + ')'
+# Insert the data into the database
+for log_entry in traffic:
+    #print log_entry
+    #print '\n'
+    data_list = []
+    for key, data in log_entry.items():
+        data_list.append(data)
+    cursor.execute(data_insertion, data_list)
+
+#selection_query = 'select * from ' + table_name
+#cursor.execute(selection_query)
+
+db_conn.commit()
+db_conn.close()
+        

### 2015-07-29 codebase/case_study/json_to_sqlite.py
Identify message templates of messages with regular expression

@@ -1,7 +1,73 @@
 # -*- coding: utf-8 -*-
 
+import sys
+import dateutil.parser as dparser
+import datetime
+import pytz
+import re
+
 import json
 import sqlite3
+
+from template import log_templates
+
+# Openstack log patterns
+log_templates = [
+        {
+            'id': 0,
+            #'body': "(OS_NUMBER) accepted ('OS_IP', OS_NUMBER)"
+            'body': "\[-\] \((\d+)\) accepted \('(\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})', (\d+)\)",
+            'variables': ['OS_NUMBER', 'OS_IP', 'OS_NUMBER2']
+        },
+        {
+            'id': 1,
+            #'body': "[-] Starting new HTTP connection (OS_NUMBER): OS_IP"
+            'body': "\[-\] Starting new HTTP connection \((\d+)\): (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
+            'variables': ['OS_NUMBER', 'OS_IP']
+        },
+        {
+            'id': 3, 
+            #'body': "[-] Auditing locally available compute resources"
+            'body': "\[-\] Auditing locally available compute resources",
+            'variables': []
+        },
+        {
+            'id': 4, 
+            #'body': "[-] Free ram (MB): OS_NUMBER"
+            'body': "\[-\] Free ram \(MB\): (\d+)",
+            'variables': ['OS_NUMBER']
+        },
+        {
+            'id': 5, 
+            #'body': "[-] Free disk (GB): OS_NUMBER"
+            'body': "\[-\] Free disk \(GB\): (\d+)",
+            'variables': ['OS_NUMBER']
+        },
+        {
+            'id': 6, 
+            #'body': "[-] Free VCPUS: OS_NUMBER"
+            'body': "\[-\] Free VCPUS: (\d+)",
+            'variables': ['OS_NUMBER']
+        },
+        {
+            'id': 8, 
+            #'body': "[-] Compute_service record updated for OS_IP:OS_IP"
+            'body': "\[-\] Compute_service record updated for OS_IP: (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
+            'variables': ['OS_IP']
+        },
+        {
+            'id': 13, 
[…]

### 2015-07-29 codebase/case_study/template_obs.py

@@ -1,0 +1,51 @@
+log_templates = [
+        {
+            'id': 0,
+            #'body': "(OS_NUMBER) accepted ('OS_IP', OS_NUMBER)"
+            'body': "\[-\] \((\d+)\) accepted \('(\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})', (\d+)\)",
+            'variables': ['OS_NUMBER', 'OS_IP', 'OS_NUMBER2']
+        },
+        {
+            'id': 1,
+            #'body': "[-] Starting new HTTP connection (OS_NUMBER): OS_IP"
+            'body': "\[-\] Starting new HTTP connection \((\d+)\): (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
+            'variables': ['OS_NUMBER', 'OS_IP']
+        },
+        {
+            'id': 3, 
+            #'body': "[-] Auditing locally available compute resources"
+            'body': "\[-\] Auditing locally available compute resources",
+            'variables': []
+        },
+        {
+            'id': 4, 
+            #'body': "[-] Free ram (MB): OS_NUMBER"
+            'body': "\[-\] Free ram \(MB\): (\d+)",
+            'variables': ['OS_NUMBER']
+        },
+        {
+            'id': 5, 
+            #'body': "[-] Free disk (GB): OS_NUMBER"
+            'body': "\[-\] Free disk \(GB\): (\d+)",
+            'variables': ['OS_NUMBER']
+        },
+        {
+            'id': 6, 
+            #'body': "[-] Free VCPUS: OS_NUMBER"
+            'body': "\[-\] Free VCPUS: (\d+)",
+            'variables': ['OS_NUMBER']
+        },
+        {
+            'id': 8, 
+            #'body': "[-] Compute_service record updated for OS_IP:OS_IP"
+            'body': "\[-\] Compute_service record updated for OS_IP: (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
+            'variables': ['OS_IP']
+        },
+        # {
+        #     'id': 13, 
[…]

### 2015-07-29 codebase/case_study/tokenize_example.py

@@ -1,0 +1,45 @@
+import sys
+import ast
+import re
+import pprint
+pp = pprint.PrettyPrinter()
+templates = [
+        {
+        'id': 0,
+        #'body': "(OS_NUMBER) accepted ('OS_IP', OS_NUMBER)"
+        'body': "\[-\] \((\d+)\) accepted \('(\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})', (\d+)\)",
+        'variables': ['OS_NUMBER', 'OS_IP', 'OS_NUMBER2']
+        },
+        {
+        'id': 1,
+        #'body': "[-] Starting new HTTP connection (OS_NUMBER): OS_IP"
+        'body': "\[-\] Starting new HTTP connection \((\d+)\): (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
+        'variables': ['OS_NUMBER', 'OS_IP']
+        },
+        {
+        'id': 3, 
+        #'body': "[-] Auditing locally available compute resources"
+        'body': "\[-\] Auditing locally available compute resources",
+        'variables': []
+        }
+        ]
+
+
+for t in templates: 
+    t['regex'] = re.compile(t['body'])
+
+messages = ast.literal_eval(''.join([l for l in sys.stdin]))
+
+for mi, m in enumerate(messages): 
+    m['id'] = -1
+    for t in templates:
+        matched = t['regex'].match(m['message_body'])
+        if matched: 
+            m['message_body_template_id'] = t['id']
+            for vi, v in enumerate(t['variables']): 
+                m['message_body' + '_' + v] = matched.group(vi + 1)
+            #if t['id'] in [1]: 
+            pp.pprint(m) 
+            break
+         
+

### 2015-07-29 paper.tex
All templates of novadelete have been input

@@
 
-\title{Declarative Data Analytic}
+\title{Knowledge discovery in networked systems}
 \author{}
@@
 and $vm_2$. To do this, a candidate specification would be ``machine\_name =
-$vm_1$. This specification is still in the scope of \saf{}. Based on this, the
+$vm_1$''. This specification is still in the scope of \saf{}. Based on this, the
 specification over the logs is similar to specification over the directory paths
@@
 
+\subsection{7/29}
+\label{sec:meeting:729}
+
+In today's meeting, we discussed about the case study of Openstack logs. Based
+on the discussion, further steps were proposed to continue the project.
+
+\paragraph{Todo}
+\begin{itemize}
+\item Finish the case study of novadelete.
+\item Re-do the case study on novaboot.
+\item Develop back-tracking and forward-tracking utilities:
+  back-tracking(event\_seed, model) = matched part of the model.
+\item Develop component-level behavior model.
+\item Develop NFA-based specification of behavior models.
+\end{itemize}
+
 \section{Root cause analysis case studies}
@@
 \begin{itemize}
-\item Backtracking the execution according to causality relationship
+\item Use SAF to analyze Openstack logs.
   \begin{itemize}
@@
   \item Convert the log in JSON into an SQLite3 database. (done)
+  \item Convert the log in JSON into an event sqlite3 database required by \saf{}.
+    \begin{itemize}
+    \item The schema of the database should satisfy the format of the event in
+      \saf{}.
+
+      As stated in ``SAF-trunk/plugins/p2db/eventattrs.c'' in p2db plugin of \saf{}: ``Each line of
+      attribute is of the following format $\langle$attributename,
+      attributetype$\rangle$ ... Each event specification must have the
+      following attributes at a minimum "eventno integer", "eventtype text",
+      "timestamp integer",	"timestampusec integer", "origin text" ''
+
+      Bug: During the test of SAF, when the wildcard symbol---e.g.,
+      port=\$1---is used in the behavior model, dependent events
+      whose field values are 0 are not output by SAF. However, if the value of a
+      field is explicitly designated as 0, dependent events will be correctly
+      output.
+
+      Fix: the problem lie in the file
+      ``SAF-trunk/framework/common/sqlutils.py''. In line 76, SAF tests the
+      validity of a value by ``if (newv):'', this causes the problem that when
+      the value of a field is 0 in dependent events, it will not be
+      processed. On the other hand, if the user explicitly specifies the value
+      of the field as 0, SAF will convert the value into string ``0'', which
+      is accepted by the conditional.
+    \item The information extracted from JSON is of coarse granularity. Further
+      parsing is needed to obtain detailed information, such as IP addresses,
+      device ids.
+
+    \item Sort the log information according to logs' timestamps. (The original
+      log is already in the correct order)
+    \end{itemize}
+
   \item Obtain domain-specific knowledge about OpenStack and the execution:

### 2015-07-29 codebase/case_study/json_to_sqlite.py

@@ -60,12 +60,92 @@ log_templates = [
             #'body': "[req-OS_UUID OS_UUID_PLAIN OS_UUID_PLAIN] OS_IP "GET /vOS_NUMBER/OS_UUID_PLAIN/servers/OS_UUID HTTP/OS_NUMBER" status: OS_NUMBER len: OS_NUMBER time: OS_NUMBER"
             'body': "\[req-([\w\-]+) (\w+) (\w+)\] (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3}) \\\"GET /v(\d+)/(\w+)/servers/([\w\-]+) HTTP/(\d+\.\d+)\\\" status: (\d+) len: (\d+) time: (\d+\.\d+)",
             'variables': ['OS_UUID', 'OS_UUID_PLAIN', 'OS_UUID_PLAIN', 'OS_IP', 'OS_NUMBER', 'OS_UUID_PLAIN', 'OS_UUID', 'OS_NUMBER', 'OS_NUMBER', 'OS_NUMBER', 'OS_NUMBER']
-        }
+        },
+        {
+            'id': 25, 
+            #'body': "[-] Lifecycle event OS_NUMBER on VM OS_UUID"
+            'body': "\[-\] Lifecycle event (\d+) on VM ([\w\-]+)",
+            'variables': ['OS_NUMBER', 'OS_UUID']
+        },
+        {
+            'id': 27, 
+            #'body': "[-] image OS_UUID at (/var/lib/nova/instances/_base/OS_UUID_PLAINOS_NUMBERcbfOS_NUMBER): checking"
+            'body': "\[-\] image ([\w\-]+) at \(/var/lib/nova/instances/_base/(\w+)(\d+)cbf(\d+)\): checking",
+            'variables': ['OS_UUID', 'OS_UUID_PLAIN', 'OS_NUMBER', 'OS_NUMBER']
+        },
+        {
+            'id': 28, 
+            #'body': "[-] image OS_UUID at (/var/lib/nova/instances/_base/OS_UUID_PLAINOS_NUMBERcbfOS_NUMBER): in use: on this node OS_NUMBER local, OS_NUMBER on other nodes sharing this instance storage"
+            'body': "\[-\] image ([\w\-]+) at \(/var/lib/nova/instances/_base/(\w+)(\d+)cbf(\d+)\): in use: on this node (\d+) local, (\d+) on other nodes sharing this instance storage",
[…]

### 2015-07-30 codebase/case_study/json_to_sqlite.py
Finish case study of novadelete

@@ -59,7 +59,7 @@ log_templates = [
             'id': 13, 
             #'body': "[req-OS_UUID OS_UUID_PLAIN OS_UUID_PLAIN] OS_IP "GET /vOS_NUMBER/OS_UUID_PLAIN/servers/OS_UUID HTTP/OS_NUMBER" status: OS_NUMBER len: OS_NUMBER time: OS_NUMBER"
             'body': "\[req-([\w\-]+) (\w+) (\w+)\] (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3}) \\\"GET /v(\d+)/(\w+)/servers/([\w\-]+) HTTP/(\d+\.\d+)\\\" status: (\d+) len: (\d+) time: (\d+\.\d+)",
-            'variables': ['OS_UUID', 'OS_UUID_PLAIN', 'OS_UUID_PLAIN', 'OS_IP', 'OS_NUMBER', 'OS_UUID_PLAIN', 'OS_UUID', 'OS_NUMBER', 'OS_NUMBER', 'OS_NUMBER', 'OS_NUMBER']
+            'variables': ['OS_UUID2', 'OS_UUID_PLAIN', 'OS_UUID_PLAIN2', 'OS_IP', 'OS_NUMBER', 'OS_UUID_PLAIN3', 'OS_UUID', 'OS_NUMBER2', 'OS_NUMBER3', 'OS_NUMBER4', 'OS_NUMBER5']
         },
         {
             'id': 25, 
@@ -71,19 +71,19 @@ log_templates = [
             'id': 27, 
             #'body': "[-] image OS_UUID at (/var/lib/nova/instances/_base/OS_UUID_PLAINOS_NUMBERcbfOS_NUMBER): checking"
             'body': "\[-\] image ([\w\-]+) at \(/var/lib/nova/instances/_base/(\w+)(\d+)cbf(\d+)\): checking",
-            'variables': ['OS_UUID', 'OS_UUID_PLAIN', 'OS_NUMBER', 'OS_NUMBER']
+            'variables': ['OS_UUID', 'OS_UUID_PLAIN', 'OS_NUMBER', 'OS_NUMBER2']
         },
         {
             'id': 28, 
             #'body': "[-] image OS_UUID at (/var/lib/nova/instances/_base/OS_UUID_PLAINOS_NUMBERcbfOS_NUMBER): in use: on this node OS_NUMBER local, OS_NUMBER on other nodes sharing this instance storage"
[…]

### 2015-07-31 codebase/case_study/template_obs.py
Wrap up the case study of novadelete

@@ -1,51 +1,0 @@
-log_templates = [
-        {
-            'id': 0,
-            #'body': "(OS_NUMBER) accepted ('OS_IP', OS_NUMBER)"
-            'body': "\[-\] \((\d+)\) accepted \('(\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})', (\d+)\)",
-            'variables': ['OS_NUMBER', 'OS_IP', 'OS_NUMBER2']
-        },
-        {
-            'id': 1,
-            #'body': "[-] Starting new HTTP connection (OS_NUMBER): OS_IP"
-            'body': "\[-\] Starting new HTTP connection \((\d+)\): (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
-            'variables': ['OS_NUMBER', 'OS_IP']
-        },
-        {
-            'id': 3, 
-            #'body': "[-] Auditing locally available compute resources"
-            'body': "\[-\] Auditing locally available compute resources",
-            'variables': []
-        },
-        {
-            'id': 4, 
-            #'body': "[-] Free ram (MB): OS_NUMBER"
-            'body': "\[-\] Free ram \(MB\): (\d+)",
-            'variables': ['OS_NUMBER']
-        },
-        {
-            'id': 5, 
-            #'body': "[-] Free disk (GB): OS_NUMBER"
-            'body': "\[-\] Free disk \(GB\): (\d+)",
-            'variables': ['OS_NUMBER']
-        },
-        {
-            'id': 6, 
-            #'body': "[-] Free VCPUS: OS_NUMBER"
-            'body': "\[-\] Free VCPUS: (\d+)",
-            'variables': ['OS_NUMBER']
-        },
-        {
-            'id': 8, 
-            #'body': "[-] Compute_service record updated for OS_IP:OS_IP"
-            'body': "\[-\] Compute_service record updated for OS_IP: (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
-            'variables': ['OS_IP']
-        },
-        # {
-        #     'id': 13, 
[…]

### 2015-08-06 paper.tex
Finish case study of novadelete
Casestudy on novaboot

@@
 \begin{itemize}
-\item Use SAF to analyze Openstack logs.
+\item Use SAF to analyze Openstack logs. All related files can be found under
+  ``declarative-log-analytics/codebase/case_study/novaboot''.
   \begin{itemize}
@@
 
-      Fix: the problem lie in the file
+      Fix: the problem lies in the file
       ``SAF-trunk/framework/common/sqlutils.py''. In line 76, SAF tests the
@@
     \item The information extracted from JSON is of coarse granularity. Further
-      parsing is needed to obtain detailed information, such as IP addresses,
-      device ids.
+      parse values in the ``message\_body'' to extract OS\_UUID, OS\_IP and
+      template id, and store them in the event table.(done)
 
@@
     data/models(Filtered Message Sequence)
+  \item Understand syntax of \saf{} behavior models
+    \begin{itemize}
+    \item Read README files
+    \item Read the source parser
+    \end{itemize}
   \item Specify the domain-specific knowledge in SAF --- on different levels ---
-    and found corresponding traces.
+    and found corresponding traces. (done with event-level behavior models)
     \begin{itemize}
@@
     \end{itemize}
-  \item Build the causality graph for different levels.
+  \item \sout{Build the causality graph for different levels.}
   \end{itemize}
-\item Root cause detection of failure symptoms based on the backtracking technique
+\item \sout{Root cause detection of failure symptoms based on the backtracking technique}
+\end{itemize}
+
+\section{Unsolved problems}
+\label{sec:usp}
+
+We list a number of identified but unsolved problems of the project.
+
+\begin{itemize}
+\item Results given by \saf{} do not always meet expectation. For example, if a
+behavior model specifies chained dependency for a specific field, \saf{} does
+not give a sequence of events, but returns the same event for each matched state
+model.
+
+\item In the log trace of boot-0.log, the message of template 17 and the message
+  of template 15 share the same timestamp. This causes the log trace to match no
+  template in the novaboot models. (17 and 15 should be reversed)
+
 \end{itemize}

### 2015-08-06 codebase/case_study/novaboot/json_to_events_boot.py

@@ -1,0 +1,395 @@
+# -*- coding: utf-8 -*-
+
+import sys
+import dateutil.parser as dparser
+import datetime
+import pytz
+import re
+
+import json
+import sqlite3
+
+# Openstack log patterns
+log_templates = [
+        {
+            'id': 0,
+            #'body': "(OS_NUMBER) accepted ('OS_IP', OS_NUMBER)"
+            'body': "\[-\] \((\d+)\) accepted \('(\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})', (\d+)\)",
+            'variables': ['OS_NUMBER', 'OS_IP', 'OS_NUMBER1']
+        },
+        {
+            'id': 1,
+            #'body': "[-] Starting new HTTP connection (OS_NUMBER): OS_IP"
+            'body': "\[-\] Starting new HTTP connection \((\d+)\): (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3})",
+            'variables': ['OS_NUMBER', 'OS_IP']
+        },
+        {
+            'id': 2,
+            #'body': "[req-OS_UUID OS_UUID_PLAIN OS_UUID_PLAIN] OS_IP "GET /vOS_NUMBER/OS_UUID_PLAIN/images HTTP/OS_NUMBER" status: OS_NUMBER len: OS_NUMBER time: OS_NUMBER"
+            'body': "\[req-([\w\-]+) (\w+) (\w+)\] (\d{1,3}\.\d{1,3}\.\d{1,3}\.\d{1,3}) \"GET /v(\d+)/(\w+)/images HTTP/(\d+\.\d+)\" status: (\d+) len: (\d+) time: (\d+\.\d+)",
+            'variables': ['OS_UUID', 'OS_UUID_PLAIN', 'OS_UUID_PLAIN1', 'OS_IP', 'OS_NUMBER', 'OS_UUID_PLAIN2', 'OS_NUMBER1', 'OS_NUMBER2', 'OS_NUMBER3', 'OS_NUMBER4']
+        },
+        {
+            'id': 3, 
+            #'body': "[-] Auditing locally available compute resources"
+            'body': "\[-\] Auditing locally available compute resources",
+            'variables': []
+        },
+        {
+            'id': 4, 
+            #'body': "[-] Free ram (MB): OS_NUMBER"
[…]

### 2015-08-20 paper.tex
Update the technical report and update the new database file

@@
 \item Use SAF to analyze Openstack logs. All related files can be found under
-  ``declarative-log-analytics/codebase/case_study/novaboot''.
+  ``declarative-log-analytics/codebase/case\_study/novaboot''.
   \begin{itemize}
@@
   template in the novaboot models. (17 and 15 should be reversed)
+
+\end{itemize}
+
+\section{Code review comments}
+\label{sec:codereview}
+
+\begin{itemize}
+\item Code logic: 
+  \begin{enumerate}
+  \item Create the event database from the database file (line 175).
+  \item Create the global symbol table
+  \item Parse the given model
+    \begin{enumerate}
+    \item parse header
+    \item parse behavior
+    \item parse model 
+    \item (What's the difference between model and behavior?A: Model = combination of behaviors)
+    \end{enumerate}
+  \item Apply the parsed model over the data to get instances.
+    \begin{enumerate}
+    \item Create StateManager
+    \item Create datahandle
+    \item Create ModelProcessor
+      \begin{enumerate}
+      \item StateProcessor
+      \item BehaviorConstraintProcessor
+      \item LTLOpsProcessor
+      \item ITLOpsProcessor
+      \item LogicalOpsProcessor
+      \end{enumerate}
+    \item Apply models to the event database to fetch satisfying data (line 287)
+    \end{enumerate}
+  \end{enumerate}
+\item Error: In behaviorinstance.py: comments for function definitions
+  ``set\_dependee'' and ``get\_dependee''. Instead of ``the pointer to the
+  behavior object'', should be ``the pointer to the dependent instance''.
+\item Error: In dataabstraction.py: comments for the function
+  ``get\_binstances\_satisfying\_state''. Instead of ``Returns a
+  BehaviorInstanceList of instances'', should be ``Returns a
+  BehaviorInstance(EventGroup) of instances''
+\item Observation: To specify dependent fields in a state proposition, the field
+  should have been mentioned by the state on which the current state is
+  dependent. For example, ``event\_1 = {ip = \$1} event\_2 = {ip =
+    event\_1.ip}'' is acceptable. But in ``event\_1 = {uuid = \$1} event\_2 = {ip =
+    event\_1.ip}'', ``event\_2'' will be recognized as an independent state.
+\item Question: Why is it that when looking for satisfying instances against a
+  specific behavior, \saf{} will produce several sub-behaviors which is copy of
+  the main behavior? For example, when processing NOVABOOTCOPY, \saf{} produces
+  a number of copies: USERMODELS.NOVABOOTCOPY.p381526;
+  USERMODELS.NOVABOOTCOPY.b;
+  USERMODELS.QUALIFIER;USERMODELS.NOVABOOTCOPY.p551410;
+  USERMODELS.NOVABOOTCOPY.p536560; USERMODELS.NOVABOOTCOPY.p989555?
 
